---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hciplusbrief

<!-- badges: start -->
<!-- badges: end -->

hciplusbrief provides lightweight, publication-ready visuals for HCI+ briefs and reporting.
A key feature is the HCI+ progress bubble chart, which compares potential (maximum) HCI+ to achieved HCI+.

## Installation

You can install the development version of hciplusbrief from [GitHub](https://github.com/) with:

```{r, eval = F}
# install.packages("pak")
pak::pak("fbw1/hciplusbrief")
```

## Example

### HCI+ progress bubble chart
The progress bubble chart displays:
- an outer bubble for Potential Productivity (max HCI+);
- an inner bubble for Actual HCI+ (progress toward the max).

The inner bubble is scaled so that its area is proportional to `progress / max_value`.


```{r example}
library(hciplusbrief)

progress_bubble_hci(
  progress = 280,
  max_value = 325,
  title = "HCI+"
)
```

